%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[margin, centered]{res}
\topmargin=-0.5in
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.5in
\itemsep=0in
\parsep=0in
\newsectionwidth{1in}
\usepackage[pdftex]{graphicx}
\usepackage{enumitem}
\usepackage{wrapfig}
\usepackage{helvet}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\setlength{\textwidth}{6.5in} % Text width of the document
\setlength{\textheight}{720pt}

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------\
\begin{center}
    \hspace{-\hoffset}
    \huge\bf{\href{http://www.pandusonu.com}{Gollapudi Vamsi Krishna}}
\end{center}
\vspace{-7mm}
\moveleft\hoffset\vbox{\hrule width 19cm height 0.5pt}
\vspace{-9mm}
\begin{center}
    \hspace{-\hoffset}
    \href{mailto:pandu.sonu@yahoo.com}{pandu.sonu@yahoo.com} ~\textbullet~ \(+91\) 9493401958 ~\textbullet~ \#338, Hall 1, National Institute of Technology, Durgapur, India
\end{center}
\vspace{-7mm}
\begin{resume}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Education}
\textbf{B.Tech in Information Technology, Third Year} \hfill 2014 - Present \\
\href{http://nitdgp.ac.in/}{National Institute of Technology Durgapur, West Bengal, India}
\begin{itemize}
 \item CGPA of \textbf{8.35}/10 (At the end of 2nd year)
\end{itemize}
\textbf{High School} - Vijaya Ratna Junior College, Hyderabad (BIE) - 95\% \hfill 2012 - 2014 \\
\textbf{Secondary School} - St. Theresa High School, Hyderabad (ICSE) - 87\% \hfill 2002 - 2012
 
%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Experience}
\textbf{Google Summer of Code Intern, \href{https://summerofcode.withgoogle.com/archive/2016/projects/5194537727164416/}{GNOME}} \hfill May, 2016 - August, 2016\\
Implementation of Week-view in GNOME-calendar. Worked with GObjects and used GTK. Also worked extensively with GIT and XML to achieve my goals.   \\
\\
\textbf{Software Engineering Intern, \href{http://www.imuneem.com/}{iMuneem}} \hfill April, 2016 - October, 2016\\
Worked with Qt framework to build the company product. Also had exposure to chrome extensions and Symfony framework to expand the company's services. 

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{Technical \hspace{2mm} Skills}
\textbf{Strongest Areas} - Algorithms, Databases, Version Control\\
\textbf{Languages} - Java, C, Python, Shell Script, C++, JS, C\#\\
\textbf{Tools/Frameworks} - GIT, Gtk, Qt, \LaTeX, MySQL, Linux, Visual Studio, Android Studio, Java util

%----------------------------------------------------------------------------------------
%	RELEVANT COURSE SECTION
%----------------------------------------------------------------------------------------
\section{Relevant \hspace{2mm} Courses}
Data Structures and Algorithms (2 courses), Operating System, Computational Mathematics, Database Management Systems, Computer Networks, Theory of Computation, Communication Systems, Computer Organization and Architecture

%----------------------------------------------------------------------------------------
%	Selected Projects Section
%----------------------------------------------------------------------------------------
\section{Selected Projects}
Some of the projects available on git : \url{https://www.github.com/pandusonu2}
\begin{itemize}[leftmargin=*]
 \item \textbf{\href{https://github.com/NIT-dgp/manga}{Manga Downloader}} :\\
 Wrote a Shell script to download and save entire manga chapters in system. Also the maintainer of the same in Github NIT-dgp organizaion.
 \item \textbf{Competitive Coding Practice} :\\
 Used Chrome developer tools to find the APIs used by codechef. Used the same, for making a tracker of the number of questions solved.
 \item \textbf{\href{https://github.com/pandusonu2/game-off-2016}{Hack The Zombies}} :\\
 Made a game using pygame for the November Github Game Off 2016 challenge.
 \item \textbf{Work on semantic web} :\\
 Implemented a better way to store rdf graphs which enables for faster sparql query processing.\\
 (Paper on the same accepted for IEEE ICSC 2017 San Diego conference)
\end{itemize}

%----------------------------------------------------------------------------------------
%	ACHIEVEMENT SECTION
%----------------------------------------------------------------------------------------

\section{Achievements}
\begin{itemize}[leftmargin=*]
 \item Selected for \href{acm.iitkgp.ac.in}{ACM ICPC Kharagpur Onsite} Regionals in 2016
 \item Maintainer at \href{https://github.com/NIT-dgp}{NIT-dgp} Open Source Organization
\end{itemize}

%----------------------------------------------------------------------------------------
%	COMPETITIVE PROGRAMMING SECTION
%----------------------------------------------------------------------------------------

\section{Competitive Programming}
\begin{itemize}[leftmargin=*]
 \item \href{https://www.topcoder.com/members/pandusonu/details/?track=DATA_SCIENCE&subTrack=SRM}{TopCoder} : Highest Rated 1,278 (Blue Color)
 \item \href{http://codeforces.com/profile/pandusonu}{CodeForces} : Highest Rated 1,692 (Blue Color)
 \item \href{https://www.codechef.com/users/pandusonu}{CodeChef} : Highest Rated 11,455 in Long (World Rank of 290 and Country Rank of 153)
 \item \href{https://code.google.com/codejam/contest/11274486/scoreboard#sp=331}{CodeJam} : Ranked 355 in Google APAC 2016 Round A
 \item Solved 100+ LeetCode and 60+ Project Euler problems
\end{itemize}

%----------------------------------------------------------------------------------------
%	HOBBIES SECTION
%----------------------------------------------------------------------------------------

\section{Hobbies}
Competitive Coding, Youtube surfing, Hanging out on Github, Solving Puzzles, Reading Novels

\section{More}
Please visit \href{http://www.pandusonu.com}{http://www.pandusonu.com}

\end{resume}
\end{document}