%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper]{deedy-resume} % Use US Letter paper, change to a4paper for A4

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

% \lastupdated % Print the Last Updated text at the top right

\namesection{Vamsi Krishna}{Gollapudi}{ % Your name
% \urlstyle{same}\url{http://www.pandusonu.com} | % Your website, LinkedIn profile or other web address
\href{mailto:pandusonu13@gmail.com}{pandusonu13@gmail.com} | +91-9493401958 %| \href{http://www.pandusonu.com}{www.pandusonu.com}  % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education}

\subsection{National Insitute of}
\subsection{Technology}

\descript{B.Tech in Information Technology}
\location{Grad. June 2018}
\location{Durgapur, West Bengal}
\location{Cum. GPA: 8.23}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{Vijaya Ratna Junior}
\subsection{College}
\descript{Intermediate education}
\location{Grad. May 2014 | Hyderabad, India}
\location{950/1000}

\sectionspace % Some whitespace after the section

\subsection{St. Theresa High School}

\descript{I.C.S.E}
\location{Grad. May 2012 | Hyderabad, India}
\location{ 610/700 }

\sectionspace

%------------------------------------------------
% Links
%------------------------------------------------

\section{Links}

Github:// \href{https://github.com/pandusonu2}{\bf pandusonu2} \\
LinkedIn:// \href{https://www.linkedin.com/in/pandusonu}{\bf pandusonu} \\
Facebook:// \href{https://www.facebook.com/pandu.sonu}{\bf pandusonu} \\
% Twitter:// \href{https://twitter.com/realPanduSonu} {\bf realPanduSonu}

\sectionspace % Some whitespace after the section

\section{Skills}

\sectionspace

\subsection{Programming}
\subsection{Contests}
(All usernames: pandusonu) \\
\location{Peak Ratings:}
\href{https://www.codechef.com/users/pandusonu}{Codechef}: 2297(orange)\\
\href{http://codeforces.com/profile/pandusonu}{Codeforces}: 1892(blue) \\
\href{https://www.topcoder.com/members/pandusonu/}{Topcoder}: 1345(blue)\\

\sectionspace

\location{Selected Ranks:}
Topcoder: 3 (Div 2 SRM 712)\\
Codeforces: 7 (Div 2, \#478)\\
Codechef LunchTime: 19 (LTIME53)\\
Codechef long: 81 (AUG16)\\
Codechef Cook-Off: 87 (COOK87)

\sectionspace

\subsection{Programming}

\location{Experienced:}
Java \textbullet{} Shell \textbullet{} Python \textbullet{} \\
C \textbullet{} Django \textbullet{} C\# \textbullet{} Kotlin

\sectionspace

\location{Familiar:}
JavaScript \textbullet{} \LaTeX \textbullet{} Rails \textbullet{} \\
Android Studio \textbullet{} Rust \textbullet{} Dart



%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{Amazon}
\descript{| Software Development Engineer}

\location{August 2018 – Present | Banglore, India}
\vspace{\topsep}
\begin{tightitemize}
\item Part of \textbf{Amazon Pay} team.
\item Worked on new registration system for Merchants in US and Japan, increasing registration completion rate by app. 10\%
\item Also worked on Seller Central of Amazon Pay and Alexa Donations.
\item Additionally was mentor to an intern.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%----------------

\runsubsection{ShareChat}
\descript{| Android Developer Intern}

\location{June 2018 – July 2018 | Banglore, India}
\begin{tightitemize}
\item Part of the \textbf{Engagement team}, worked to increase user retention to 75\%
\item Worked on enhancing the applicaton by modifying user experience with features like Vertical Scroll bar and enchanched comment/like/share section.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%-----------------

\runsubsection{Amazon}
\descript{| SDE Intern}

\location{May 2017 – July 2017 | Bangalore, India}
\begin{tightitemize}
\item Created package for centralizing global data for the \textbf{US and Japan Amazon Pay} systems.
\item Resulted in the removal of duplicate items, making the overall product more maintainable and scalable.
\item Also, significant UI changes were also done by me during the period.
%\item Was offered a PPO based on the performance.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{GNOME}
\descript{| Google Summer of Code Intern}

\location{April 2016 – Aug 2016 | Online}
\begin{tightitemize}
\item Worked on gnome calendar, initializing the essential \textbf{week-view} feature in it.
\item It is a part of official Ubuntu release from Ubuntu 17.10, used by app 70 mil users.
\item This was one of projects selected for Google Summer of Code, sponsored by Google.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Projects
%------------------------------------------------

\section{Projects}

\runsubsection{Speak Code}
\descript{| Microsoft Imagine Cup National Finalist}

\location{Jan 2017 - Present}
Developed a Windows application to help learn to code in any spoken language. \\
Backend written in Ruby on Rails, by using an open soured Online judge. \\
This was one of the only 30 projects selected for the Indian National finals of Microsoft Imagine Cup 2k17. \\
Link to youtube video: \href{https://www.youtube.com/watch?v=hO4iSh1bSC0}{Speak Code}

\sectionspace

%\runsubsection{Manga downloader}
%\descript{| Open Source Collabration}

%\location{March 2015 - Present}
%Group of bash scripts used to download, convert and save comics from online sources.\\
%This was forked and starred multiple times in GitHub, with collabration of students across India.\\
%Primary maintainer of the overall product as part of NIT Dgp Open Source group. \\
%Link to repo: \href{https://github.com/NITDgpOS/manga}{Manga Downloader}

%\sectionspace

%\runsubsection{F1 type ranklist}
%\descript{| Django}

%\location{Aug 2017 - Present}
%Discovered codechef APIs using Google Chrome tools and used the same to generate customized ranklist from codechef. \\
%Link to repo: \href{https://github.com/pandusonu2/Codechef-f1-ranklist}{Codechef F1 ranklist}

%\sectionspace

%------------------------------------------------
% Research
%------------------------------------------------

\section{Research}

\runsubsection{Algorithms}

\location{April 2017 - June 2018}
Project based on complete set partitioning for collation structure generation.\\
Compared existing heuristic algorithms and created a new approach using Dynamic Programming.\\
Polynomial runtime giving an answer with an error rate of 10\% of the optimal answer.

\sectionspace

% \runsubsection{Semantic Web}

% \location{Oct 2015 - March 2016}
% Developed new graph models to assert meta knowledge in web of data. \\
% Paper accepted in IEEE ICSC 2017. [Paper later withdrawn due to lack of funds]

\sectionspace

%------------------------------------------------
% Awards
%------------------------------------------------

\section{Additional activities and Hackathons}

\sectionspace

\begin{tightitemize}
\item National finalist of Code-N-Counter 2.0 organized by Nagarro\\
\item National finalist of Humblefool cup 2017 organized by topcoder\\
\item Qualified for ACM ICPC regionals in 2016 and 2017\\
\item Founding member of \href{https://github.com/NITDgpOS}{NITDgpOS}
\end{tightitemize}

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

\end{document}
